---
title: "Untitled"
description: |
  A new article created using the Distill format.
author:
  - name: Nora Jones 
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: distill::distill_article
params:
  interactive: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set()
```

```{r setup_interactive, eval=params$interactive, include=FALSE}
source("libraries.R")
```

# Idea

In Tour de France history, time trials always are a spectacle of their own.
Oftentimes they are a decisive factor on who wins the general classification of
an edition. This was also the case this year with a stunning performance of
Jonas Vingegaard. In this post we want to look at the performance of Jonas
Vingegaard. This post is heavily inspired by this post [here](https://www.reddit.com/r/peloton/comments/153ys8r/most_dominant_tt_performances_in_the_tdf_since/?utm_source=share&utm_medium=android_app&utm_name=androidcss&utm_term=3&utm_content=share_button).

```{r, file="libraries.R", eval=FALSE}
```

# Data

Extract all urls for TdF edtions from the last years.
Scrape stages overview. Determine relevant nodes by looking for
'`r tar_read(stages_urls_css)`'.

```{r, file="R/stages_overview_raw.R"}
```

```{r, echo=FALSE}
tar_read(df_stages_overview_combined_raw)
```

Filter for time trial stages. Keep only rows containing the key word
'`r tar_read(time_trial_regex)[[1]]`' to do so. After filtering, further process
the description to keep the string short and simple:

```{r, file="R/stages_itt.R"}
```

```{r, echo=FALSE}
tar_read(df_stages_itt)
```

For every time trial, scrape the result of the stage:

```{r, file="R/stage_raw.R"}
```

Preprocess stage data:

```{r, file="R/stage.R"}
```

Calculate time delta to winner time for each rider.

```{r, file="R/time_delta.R"}
```

```{r, echo=FALSE}
tar_read(df_time_delta)
```

Extract time for each winner:

```{r, file="R/winner_time.R"}
```

# Analysis

Combine everything into one data frame. Calculate total time for each rider:

```{r, file="R/total_time.R"}
```

Visualize data:

```{r, file="R/vis_total_time.R"}
```

```{r, echo=FALSE, fig.height=7, fig.width=8}
tar_read(gg_total_time)
```

