---
title: "Scraping Tour de France Data"
description: |
  An article about friendly webscraping and a remarkable Time Trial
author:
  - name: Julian During
    url: https://example.com/norajones
date: "`r Sys.Date()`"
output: distill::distill_article
preview: "https://raw.githubusercontent.com/duju211/tour_tt/master/total_time.png"
creative_commons: CC BY
repository_url: https://github.com/duju211/tour_tt
base_url: https://www.datannery.com/posts/tdf_itt/
params:
  interactive: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set()
```

```{r setup_interactive, eval=params$interactive, include=FALSE}
source("libraries.R")
```

# Idea

In Tour de France history, time trials always are a spectacle of their own.
Oftentimes they are a decisive factor on who wins the general classification
each year. This was also the case this year with a stunning performance of
Jonas Vingegaard on the 16th stage from Passy to Combloux.

In this post we want to look at the performance of Jonas
Vingegaard in more detail, heavily inspired by this post 
[here](https://www.reddit.com/r/peloton/comments/153ys8r/most_dominant_tt_performances_in_the_tdf_since/?utm_source=share&utm_medium=android_app&utm_name=androidcss&utm_term=3&utm_content=share_button).
We will scrape and visualize the data within R using the following packages:

```{r, file="libraries.R", eval=FALSE}
```

# Data

First we need the raw data. We will get the raw data from
'`r tar_read(cycling_stats_url)`.

The exact path where we will get the data, is determined by the string
'`r tar_read(stages_overview_path)`' + the year
(up until year `r tar_read(start_year)`) of the Tour de France edtion:

```{r, file="R/tdf_editions.R"}
```

```{r, echo=FALSE}
tar_read(df_tdf_editions)
```

Scrape the stage overview for each edition by using the following helper
function.
After a first introduction (next code chunk) we alter the url by adding the
path from the above code chunk.
We do this by applying the `polite::nod` function.
After the exact url is determined, we scrape the content of the webpage using
the `polite::scrape` function.

Keep only certain elements of the scraped html by looking
for CSS '`r tar_read(stages_urls_css)`'. The CSS was determined using
techniques described in this [vignette](`r tar_read(rvest_url)`).

```{r, file="R/scrape_overview.R"}
```

Before we apply this function multiple times, we first introduce ourselves with
the `polite::bow` function. After that we apply the above function to each
edition. By doing this we automatically apply to the
scraping restrictions defined in `robots.txt`.

```{r, file="R/stages_overview_raw.R"}
```

The result looks like this:

```{r, echo=FALSE}
tar_read(df_stages_overview)
```

Preprocess stages overview. Only keep rows with description and extract year
of the edition from `href`:

```{r, file="R/stages_overview.R"}
```

Filter for time trial stages. Keep only rows containing the following key word
to do so:

```{r, echo=FALSE}
tar_read(time_trial_regex)[[1]]
```

 After filtering, further process
the description to keep the string short and simple:

```{r, file="R/stages_itt.R"}
```

```{r, echo=FALSE}
tar_read(df_stages_itt)
```

For every time trial, scrape the result of the stage. Use the following helper
function. In the scraped html look for the CSS defined by
'`r tar_read(stage_tbl_css)`'.

```{r, file="R/scrape_stage.R"}
```

Again, first `bow` to the host and then apply the function from the
above code chunk repeatedly.

```{r, file="R/stage.R"}
```

```{r, echo=FALSE}
tar_read(df_stage)
```


Calculate time delta to winner time for each rider:

```{r, file="R/time_delta.R"}
```

```{r, echo=FALSE}
tar_read(df_time_delta)
```

Extract time for each winner:

```{r, file="R/winner_time.R"}
```

# Analysis

Combine everything into one data frame. Calculate total time for each rider:

```{r, file="R/total_time.R"}
```

Summarise data per stage. Use this summary to arrange the description as an
ordered factor. Exclude winner rows from the data:

```{r, file="R/total_time_summary.R"}
```

Visualize data. Arrange the stages based on the summary calculated in the
preceding code chunk:

```{r, file="R/vis_total_time.R"}
```

```{r plot_total_time, echo=FALSE}
knitr::include_graphics(tar_read(png_total_time))
```

The top stages are almost all (except for `Cap Découverte`) mountain time
trials. One can see that this years time trial stands out from the rest
nonetheless!
